---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
    citation_package: biblatex
  bookdown::html_document2: default
  bookdown::word_document2: default
documentclass: book
#bibliography: [bibliography/references.bib, bibliography/additional-references.bib]
---

# Experiment analysis

\minitoc <!-- this will include a mini table of contents-->

```{r 01-setup, echo=FALSE, message=FALSE}
include_image <- function(url_web, url_latex) {
  
  url_file <- ifelse(
    test = knitr::is_latex_output(),
    yes = url_latex,
    no = url_web
  )
  
  linguisticsdown::include_graphics2(path = url_file)
}

custom_include <- function(url_base, file_name, web_type = ".png", latex_type = ".pdf") {
  include_image(
    url_web = paste0(url_base, "figure-html/", file_name, web_type),
    url_latex = paste0(url_base, "figure-latex/", file_name, latex_type)
  )
}

main_url <- "https://raw.githubusercontent.com/jvelezmagic/CellFilamentationAnalysis/main/_bookdown_files/"
include_cells_image <- purrr::partial(
  .f = custom_include,
  url_base = paste0(main_url, "03-jvelezmagic-cell-eda_files/")
)

include_tracks_image <- purrr::partial(
  .f = custom_include,
  url_base = paste0(main_url, "04-jvelezmagic-cell-time-eda_files/")
)

knitr::opts_chunk$set(
  fig.pos = "H",
  out.width = "100%",
  echo = FALSE,
  message = FALSE
)
```

## Introduction

## Experiment design

## Exploratory Data Analysis

### General preprocessing of data

The processing of the raw data consisted mainly of creating two levels of observation for the cells of both chromosomal strains and multicopy plasmids.
The first level is at a cell granularity, that is, point properties.
The second level consists of the cells over time, thus observing properties at the population level.
We did this because it would allow us to understand what factors are affecting filamentation and why.

We decided to normalize the fluorescence values of DS-Red and GFP for both experiments based on the values observed before the start of the experiment.
It allowed us to have a basis to work with and compare the expressions between cells.
In the case of DS-Red, we also applied a logarithmic transformation to observe subtle changes that would allow us to dig deeper.

Ultimately, we decided to classify cells into four fundamental groups based on whether the cell was filamented and survived (see \@ref(fig:03-cells-distribution-across-experiments)).
We define a *filamented cell* as a cell that is more than two standard deviations from the mean concerning the lengths observed before antibiotic entry into the system [].
On the other hand, although there are multiple ways to define death in a cell context [], we decided to consider a *cell dead or missing* when we stopped having information about it, either because of its fluorescence levels or because it left the field of experimental tracking.
Therefore, a *surviving cell* is one that existed before and after the exposure to the antibiotic.

### Cells level

(ref:03-cells-distribution-across-experiments-1-scap) Cell classification and its distribution across experiments.

(ref:3-cells-distribution-across-experiments-1-cap) **Cell classification and its distribution across experiments.** We define a *filamented cell* as a cell whose length exceeded two standard deviations from the mean at any time during the experiment. A *surviving cell* is a cell that existed before and after exposure to the antibiotic. We removed from the analysis those cells that died before or were born after the exposure of the experiment. Therefore, we delimited the effect caused by the exposure to the antibiotic.

```{r 03-cells-distribution-across-experiments, fig.cap='(ref:3-cells-distribution-across-experiments-1-cap)', fig.scap='(ref:03-cells-distribution-across-experiments-1-scap)'}
include_cells_image("03-cells-distribution-across-experiments-1")
```

(ref:03-cells-life-time-classes-distribution-1-scap) Cells life time classes distribution.

(ref:03-cells-life-time-classes-distribution-1-cap) **Cells life time classes distribution.** Chromosomal cells appear to show more remarkable survival by the filamented class compared to non-filamented survivors. On the other hand, in cells with plasmids, the relationship seems to be the opposite. However, this may be due to several factors. For instance, the levels of antibiotic resistance inherent in a heterogeneous population is the most simple explanation. For each cell, we calculate its lifetime, that is, the last time we saw the cell minus the time we had our first observation of it. We truncated the time to one frame (*i.e.*, $10$ minutes) after finishing the antibiotic exposure. From the first appearance of green or purple color (*i.e.*, surviving cells), higher lifetime values represent cells that existed long before the start of the experiment.

```{r 03-cells-life-time-classes-distribution-1, fig.cap='(ref:03-cells-life-time-classes-distribution-1-cap)', fig.scap='(ref:03-cells-life-time-classes-distribution-1-scap)'}
include_cells_image("03-cells-life-time-classes-distribution-1")
```

(ref:03-division-number-divisions-1-scap) Cell's number of divisions.

(ref:03-division-number-divisions-1-cap) **Cell's number of divisions.** Chromosomal cells exhibited more divisions for surviving classes and non-surviving filamented cells (*i.e.*, purple, green, and red dots) relative to unchanged behavior in plasmid cells. Therefore, its contribution to filamentation remains uncertain.

```{r 03-division-number-divisions-1, fig.cap='(ref:03-division-number-divisions-1-cap)', fig.scap='(ref:03-division-number-divisions-1-scap)'}
include_cells_image("03-division-number-divisions-1")
```

(ref:03-division-time-since-last-division-1-scap) Time elapsed since the last division at the beginning of the experiment.

(ref:03-division-time-since-last-division-1-cap) **Time elapsed since the last division at the beginning of the experiment.** The mean time of the last division before starting the experiment indicates that it did not influence the final result for chromosomal cells. There is a slight difference between the filamented-not survived cells and the rest of the classes for cells with plasmids. However, the signal does not appear to be strong on the survival role. Therefore, we conclude that we have no evidence to support that the time of the last division at the beginning of the experiment influences the final classification results.

```{r 03-division-time-since-last-division-1, fig.cap='(ref:03-division-time-since-last-division-1-cap)', fig.scap='(ref:03-division-time-since-last-division-1-scap)'}
include_cells_image("03-division-time-since-last-division-1")
```

(ref:03-focus-just-in-initial-values-1-scap) Experiment initial values.

(ref:03-focus-just-in-initial-values-1-cap) **Experiment initial values.** By positioning a cell in space based on its initial length and GFP values, we can see that class separation occurs, but not as a strong signal. Therefore, we concluded that although the initial state influences the result, this is not everything. For this, we have the example of the length changes throughout the experiment caused by filamentation. In this graph, the GFP scale is at log10 to help us observe those minor differences between the experiments.

```{r 03-focus-just-in-initial-values-1, fig.cap='(ref:03-focus-just-in-initial-values-1-cap)', fig.scap='(ref:03-focus-just-in-initial-values-1-scap)'}
include_cells_image("03-focus-just-in-initial-values-1")
```

(ref:03-metric-differences-1-scap) Experiment initial values differences.

(ref:03-metric-differences-1-cap) **Experiment initial values differences.** By comparing the metric differences of the last observation and the first observation of a cell, we can separate mainly the surviving filamented cells from those that did not do it in both experiments (green dots). Meanwhile, cells with plasmids form a small accumulation of surviving cells that did not produce filament (purple dots). However, this has made a breakthrough in understanding what is affecting cell survival. There are still variables that we can include to understand this phenomenon better.

```{r 03-metric-differences-1, fig.cap='(ref:03-metric-differences-1-cap)', fig.scap='(ref:03-metric-differences-1-scap)'}
include_cells_image("03-metric-differences-1")
```

(ref:03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1-scap) Principal Component Analysis of chromosomal strain.

(ref:03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1-cap) **Principal Component Analysis of chromosomal strain.** When integrating the information of different variables in a dimensionality reduction analysis, we observed a clear separation between the surviving cells and those that did not. The contributions that determined this phenomenon come mainly from the last amount of DS-red, GFP, and length of the cell (see Figure \@ref(fig:03-see-datasets-individualy-pca-chromosome-variable-contribution-1)). Although it seems obvious, it effectively confirms that the temporal classification that we carry out makes sense. Thus, highlighting the importance of filamentation. Longer length represents a greater uptake of antibiotics but in a much larger volume, so the net effect is an internal reduction of antibiotics (see Figure \@ref(fig:cell-dimensions-relationship)).

```{r 03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1, fig.cap='(ref:03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1-cap)', fig.scap='(ref:03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1-scap)'}
include_cells_image("03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1")
```

(ref:03-see-datasets-individualy-pca-chromosome-variable-contribution-1-scap) Variables contribution of Principal Component Analysis of chromosomal strain.

(ref:03-see-datasets-individualy-pca-chromosome-variable-contribution-1-cap) **Variables contribution of Principal Component Analysis of chromosomal strain.** In the figure \@ref(fig:03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1), we see that the classes we created manually reflected what was observed when performing a reduction of dimensions analysis. The individual contribution of each variable for the first two components is shown here. The variables that most affected components 1 and 2 (X-axis and Y-axis, respectively) are the final measurements of DS-red, GFP, length, and the initial amount of GFP. Given that they are chromosomal strains, we should note that this variability could be produced by intrinsic experimental noise that we could not remove. With that in mind, having the DS-red and the final length highlights the inherent role of cells by having increased its size.

```{r 03-see-datasets-individualy-pca-chromosome-variable-contribution-1, fig.cap='(ref:03-see-datasets-individualy-pca-chromosome-variable-contribution-1-cap)', fig.scap='(ref:03-see-datasets-individualy-pca-chromosome-variable-contribution-1-scap)'}
include_cells_image("03-see-datasets-individualy-pca-chromosome-variable-contribution-1")
```

(ref:03-see-datasets-individualy-pca-plasmid-points-in-new-coordinates-1-scap) Principal Component Analysis of plasmid strain.

(ref:03-see-datasets-individualy-pca-plasmid-points-in-new-coordinates-1-cap) **Principal Component Analysis of plasmid strain.** By integrating the information from different variables in a dimensionality reduction analysis, we observed a clear separation between the filamented and non-filamented cells. Said class separation is given by component 2 (Y-axis), which is determined primarily by the initial and final lengths of the cells (see Figure \@ref(fig:03-see-datasets-individualy-pca-plasmid-variable-contribution-1)). Furthermore, the classification also allows us to separate those filamented cells that died from those that survived. Therefore, despite the increase in the complexity of the system, length continues to play a role in determining survival.

```{r 03-see-datasets-individualy-pca-plasmid-points-in-new-coordinates-1, fig.cap='(ref:03-see-datasets-individualy-pca-plasmid-points-in-new-coordinates-1-cap)', fig.scap='(ref:03-see-datasets-individualy-pca-plasmid-points-in-new-coordinates-1-scap)'}
include_cells_image("03-see-datasets-individualy-pca-plasmid-points-in-new-coordinates-1")
```

(ref:03-see-datasets-individualy-pca-plasmid-variable-contribution-1-scap) Variables contribution of Principal Component Analysis of plasmid strain.

(ref:03-see-datasets-individualy-pca-plasmid-variable-contribution-1-cap) **Variables contribution of Principal Component Analysis of plasmid strain.** In Figure \@ref(fig:03-see-datasets-individualy-pca-plasmid-points-in-new-coordinates-1), we saw that we could separate the filamented cells from the non-filamented ones. The reduction analysis also shows a slight difference between surviving and dead cells within the small group of filamented cells. Here we offer the individual contribution of each variable for the first two components. For the first component (x-axis in Figure \@ref(fig:03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1)), the initial and final GFP measurements received mainly the variability. We expected this component's importance since, being a chromosomal strain, we hope that its inherent variation will be inherited into the system. On the other hand, the second component (Y-axis in Figure \@ref(fig:03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1)) was determined by the length of the cell. Factors that, in the chromosomal strain (see Figure \@ref(fig:03-see-datasets-individualy-pca-chromosome-variable-contribution-1)), determined with the help of DS-red the separation between surviving and dead cells.

```{r 03-see-datasets-individualy-pca-plasmid-variable-contribution-1, fig.cap='(ref:03-see-datasets-individualy-pca-plasmid-variable-contribution-1-cap)', fig.scap='(ref:03-see-datasets-individualy-pca-plasmid-variable-contribution-1-scap)'}
include_cells_image("03-see-datasets-individualy-pca-plasmid-variable-contribution-1")
```

(ref:03-see-datasets-individualy-umap-chromosome-points-in-new-coordinates-1-scap) UMAP coordinates of chromosome strain.

(ref:03-see-datasets-individualy-umap-chromosome-points-in-new-coordinates-1-cap) **UMAP coordinates of chromosome strain.** We represented the cells in a low dimensional space. This new projection made it possible to group the cells that survived and those that did not. Therefore, as in PCA Figure \@ref(fig:03-see-datasets-individualy-pca-chromosome-points-in-new-coordinates-1), this technique supports the manual classification that we perform. However, the distance between the groups has no real meaning.

```{r 03-see-datasets-individualy-umap-chromosome-points-in-new-coordinates-1, fig.cap='(ref:03-see-datasets-individualy-umap-chromosome-points-in-new-coordinates-1-cap)', fig.scap='(ref:03-see-datasets-individualy-umap-chromosome-points-in-new-coordinates-1-scap)'}
include_cells_image("03-see-datasets-individualy-umap-chromosome-points-in-new-coordinates-1")
```

(ref:3-see-datasets-individualy-umap-plasmid-points-in-new-coordinates-1-scap) UMAP coordinates of plasmid strain.

(ref:3-see-datasets-individualy-umap-plasmid-points-in-new-coordinates-1-cap) **UMAP coordinates of plasmid strain.** As in its \@ref(fig:03-see-datasets-individualy-umap-chromosome-points-in-new-coordinates-1) pair, the representation in a low-dimensional space helped classify the cells, grouping mainly into 4 groups, 2 of survivors and 2 of non-survivors. The variable "*division*" marks the separation of classes. The *division* variable indicates whether a cell divided during its lifetime or not. Together, the UMAP represents the manually assigned classes. The distance between the groups has no real meaning.

```{r 3-see-datasets-individualy-umap-plasmid-points-in-new-coordinates-1, fig.cap='(ref:3-see-datasets-individualy-umap-plasmid-points-in-new-coordinates-1-cap)', fig.scap='(ref:3-see-datasets-individualy-umap-plasmid-points-in-new-coordinates-1-scap)'}
include_cells_image("03-see-datasets-individualy-umap-plasmid-points-in-new-coordinates-1")
```

(ref:03-temporal-metric-distribution-ds-red-1-scap) DS-red temporal distribution.

(ref:03-temporal-metric-distribution-ds-red-1-cap) **DS-red temporal distribution.** To evaluate the incident effect of the antibiotic marked by DS-red on cells by class, we show its values ​​at three key moments: start, filamentation (SOS), and end. The upper asterisks represent the significance value when comparing a group X to the filamented and surviving cell reference. Asterisks in a line indicate whether or not there is a significant difference in the survival of non-filamented cells. The black dots represent the mean of each group, and the lines that join them are a comparative guide. The extent of the black bars represents the distribution of the data. Although, at the initial time, we observe multiple significant differences, this is likely due to the intrinsic noise of the system since, as expected, the values ​​are close to zero. We observed a difference between the surviving and non-filamented cells for the chromosomal strain for the SOS time, but the same did not occur for the plasmid strain. The final amount of DS-red makes a clear difference between survival and death.

```{r 03-temporal-metric-distribution-ds-red-1, fig.cap='(ref:03-temporal-metric-distribution-ds-red-1-cap)', fig.scap='(ref:03-temporal-metric-distribution-ds-red-1-scap)'}
include_cells_image("03-temporal-metric-distribution-ds-red-1")
```

(ref:03-temporal-metric-distribution-gfp-1-scap) GFP temporal distribution.

(ref:03-temporal-metric-distribution-gfp-1-cap) **GFP temporal distribution.** To evaluate the incident effect of the GFP on cells by class we used the same notation as in Figure \@ref(fig:03-temporal-metric-distribution-ds-red-1). The chromosomal strain has significant values of GFP ​​at different times. However, these differences can be mainly due to experimental noise. We appreciated in the plasmid strain that the filamented cells had a lower amount of initial GFP as expected. At the time of filamentation, there is no difference between the survivors and the dead. However, in the end time, we observed that the surviving non-filamented cells have less GFP than the dead non-filamented and the living filamented cells.

```{r 03-temporal-metric-distribution-gfp-1, fig.cap='(ref:03-temporal-metric-distribution-gfp-1-cap)', fig.scap='(ref:03-temporal-metric-distribution-gfp-1-scap)'}
include_cells_image("03-temporal-metric-distribution-gfp-1")
```

(ref:03-temporal-metric-distribution-length-1-scap) Length temporal distribution.

(ref:03-temporal-metric-distribution-length-1-cap) **Length temporal distribution.** To evaluate the incident effect of length on cells by class, we use the same notation as in Figure \@ref(fig:03-temporal-metric-distribution-ds-red-1). The observations for both strains, chromosomal or plasmid, are the same. In the beginning, the surviving filamented cells already have a difference in length concerning the rest of the classes. At the time of filamentation, there is no difference to help determine whether the cell will survive or not. Finally, in the final time, it seems that the surviving filamented cells have a greater length than the rest of the groups. However, this length is moderate compared to the excess length shown by non-surviving filamented cells. On the other hand, we highlighted the growth of the surviving non-filamented cells. Therefore, although they did not reach a length for us to classify as filamented, the cells did resort to filamentation.

```{r 03-temporal-metric-distribution-length-1, fig.cap='(ref:03-temporal-metric-distribution-length-1-cap)', fig.scap='(ref:03-temporal-metric-distribution-length-1-scap)'}
include_cells_image("03-temporal-metric-distribution-length-1")
```

<!-- (ref:03-time-to-filamentation-all-1-scap) Time to filamentation without filters. -->

<!-- (ref:03-time-to-filamentation-all-1-cap) **Time to filamentation without filters.** -->

<!-- ```{r 03-time-to-filamentation-all-1, fig.cap='(ref:03-time-to-filamentation-all-1-cap)', fig.scap='(ref:03-time-to-filamentation-all-1-scap)'} -->
<!-- include_cells_image("03-time-to-filamentation-all-1") -->
<!-- ``` -->

(ref:03-time-to-filamentation-filamented-once-experiment-start-1-scap) Time to filamentation filtered.

(ref:03-time-to-filamentation-filamented-once-experiment-start-1-cap) **Time to filamentation filtered.** To quantify the effect of filamenting to survive, we filtered those cells that filamented during the experiment. In this way, we normalize the start times for the calculation of the filamentation time. For both strains, the filamentation time had a more significant delay in the surviving cells.

```{r 03-time-to-filamentation-filamented-once-experiment-start-1, fig.cap='(ref:03-time-to-filamentation-filamented-once-experiment-start-1-cap)', fig.scap='(ref:03-time-to-filamentation-filamented-once-experiment-start-1-scap)'}
include_cells_image("03-time-to-filamentation-filamented-once-experiment-start-1")
```

<!-- (ref:03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-diff-values-1-scap) Experiment initial values differences with time. -->

<!-- (ref:03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-diff-values-1-cap) **Experiment initial values differences with time.** -->

<!-- ```{r 03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-diff-values-1, fig.cap='(ref:03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-diff-values-1-cap)', fig.scap='(ref:03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-diff-values-1-scap)'} -->
<!-- include_cells_image("03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-diff-values-1") -->
<!-- ``` -->

(ref:03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-initial-values-1-scap) Experiment initial values with time to filamentation.

(ref:03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-initial-values-1-cap) **Experiment initial values with time to filamentation.** As in Figure \@ref(fig:03-focus-just-in-initial-values-1), including the time it will take for cells to filament allows us to understand the phenomenon of survival better. Cells that filamented and survived generally have a much higher delay than their non-filamented peers for both strains (see Figure \@ref(fig:03-time-to-filamentation-filamented-once-experiment-start-1)).

```{r 03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-initial-values-1, fig.cap='(ref:03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-initial-values-1-cap)', fig.scap='(ref:03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-initial-values-1-scap)'}
include_cells_image("03-time-to-filamentation-include-time-to-filamentation-in-initial-exploration-initial-values-1")
```

### Tracks level

(ref:04-metrics-over-time-1-scap) Population measurements over time.

(ref:04-metrics-over-time-1-cap) **Population measurements over time.** The colored lines symbolize the average value of each metric at each instant of time, while its surrounded gray shaded area represents the 95% confidence interval. The vertical lines represent the start and end of antibiotic exposure. The horizontal line in the length metric symbolizes the threshold to consider a cell filament. We observed a faster increase of DS-red for the non-surviving populations in both experiments. Regarding the GFP metric, the behavior is relatively stable for the chromosomal strain. In contrast, for the plasmid strain, a decline in GFP is observed for the population that did not survive. For the length metric, it is interesting to note how the chromosome cells that did not filament continued to grow past the filamentation threshold once the exposure to the antibiotic in the chromosomal strain had ended. On the other hand, the filamented and dead cells seem to have a greater length from the beginning for the plasmid strain.

```{r 04-metrics-over-time-1, fig.cap='(ref:04-metrics-over-time-1-cap)', fig.scap='(ref:04-metrics-over-time-1-scap)'}
include_tracks_image("04-metrics-over-time-1")
```

(ref:04-length-survival-probability-1-scap) Plasmid initial length survival probability.

(ref:04-length-survival-probability-1-cap) **Plasmid initial length survival probability.** We calculated the survival probability after comparing the population distributions of length with those of the cells that managed to survive.

```{r 04-length-survival-probability-1, fig.cap='(ref:04-length-survival-probability-1-cap)', fig.scap='(ref:04-length-survival-probability-1-scap)'}
include_tracks_image("04-length-survival-probability-1")
```

(ref:04-gfp-survival-probability-1-scap) Plasmid initial GFP survival probability.

(ref:04-gfp-survival-probability-1-cap) **Plasmid initial GFP survival probability.** We calculated the survival probability after comparing the population distributions of GFP with those of the cells that managed to survive. To assess survival by GFP, we only used plasmid cells. For non-filamented cells (blue dots), a bell forms with an upturned tail. On the other hand, for the filamented cells (red dots), a continuous increase in survival is shown just when it seems that the probability of the non-filamented cells has a decrease. In global, much GFP has higher resistance, but an average GFP value without filamentation also increases the probability of survival.

```{r 04-gfp-survival-probability-1, fig.cap='(ref:04-gfp-survival-probability-1-cap)', fig.scap='(ref:04-gfp-survival-probability-1-scap)'}
include_tracks_image("04-gfp-survival-probability-1")
```

(ref:04-cell-status-over-time-status-without-dead-1-scap) Population status over time without dead.

(ref:04-cell-status-over-time-status-without-dead-1-cap) **Population status over time without dead.**

```{r 04-cell-status-over-time-status-without-dead-1, fig.cap='(ref:04-cell-status-over-time-status-without-dead-1-cap)', fig.scap='(ref:04-cell-status-over-time-status-without-dead-1-scap)'}
include_tracks_image("04-cell-status-over-time-status-without-dead-1")
```

(ref:04-cell-status-over-time-status-with-dead-1-scap) Population status over time with dead.

(ref:04-cell-status-over-time-status-with-dead-1-cap) **Population status over time with dead.**

```{r 04-cell-status-over-time-status-with-dead-1, fig.cap='(ref:04-cell-status-over-time-status-with-dead-1-cap)', fig.scap='(ref:04-cell-status-over-time-status-with-dead-1-scap)'}
include_tracks_image("04-cell-status-over-time-status-with-dead-1")
```

(ref:04-cell-status-over-time-proportion-living-cells-by-gfp-row-1-scap) Population survivals binned by initial GFP over time.

(ref:04-cell-status-over-time-proportion-living-cells-by-gfp-row-1-cap) **Population survivals binned by initial GFP over time.**

```{r 04-cell-status-over-time-proportion-living-cells-by-gfp-row-1, fig.cap='(ref:04-cell-status-over-time-proportion-living-cells-by-gfp-row-1-cap)', fig.scap='(ref:04-cell-status-over-time-proportion-living-cells-by-gfp-row-1-scap)'}
include_tracks_image("04-cell-status-over-time-proportion-living-cells-by-gfp-row-1")
```

(ref:04-cell-status-over-time-proportion-living-cells-by-gfp-point-1-scap) Normalized population survivals binned by initial GFP over time.

(ref:04-cell-status-over-time-proportion-living-cells-by-gfp-point-1-cap) **Normalized population survivals binned by initial GFP over time.**

```{r 04-cell-status-over-time-proportion-living-cells-by-gfp-point-1, fig.cap='(ref:04-cell-status-over-time-proportion-living-cells-by-gfp-point-1-cap)', fig.scap='(ref:04-cell-status-over-time-proportion-living-cells-by-gfp-point-1-scap)'}
include_tracks_image("04-cell-status-over-time-proportion-living-cells-by-gfp-point-1")
```

## Discussion
